---
title: "Visualization of lead times generated by open Jackson networks"
author: "Nanna Burmeister"
date: "9/11/2021"
output: html_document
---
# Open Jackson networks
```{r}
set.seed(1) # Set seed for reproducibility
```

## Step 1: External arrivals
In an open Jackson network, jobs arrive from outside following a Poisson process with rate $\alpha > 0$. Then the interarrivals the system exponentially distributed with rate $\alpha > 0$.


## Step 2: M/M/1 queues
A Jackson network consists of $K$ M/M/m queues. For simplicity I have chosen $m=1$,
meaning at each node only have one server.

#Verification of M/M/1 function
```{r}
N <- 10e4
lambda <- 0.4
mu <- 0.5
# Run function
arrivals <- cbind(1:N, cumsum(rexp(N, lambda)))
output <- simulate_mm1_queue(arrivals, mu)
#Compare cummulative mean from simulation with theoretical expression of the mean
sojourn_time_sim <- mean(output$total_time)
sojourn_time_theoritical <- (1/(mu-lambda))

x <- 1:N
plot(x, cumsum(output$total_time)/x, type = "l", lty = 1)
abline(h=sojourn_time_theoritical, col="red")
```

## Step 3: Open Jackson network
Indsæt figurer.....

>>Show function<<

# Visualisation of output from the generators
```{r, message = FALSE, warning = FALSE}
source("C:/Users/Bruger/Documents/P8/Projekt/R/src/mm1_queue.R")
source("C:/Users/Bruger/Documents/P8/Projekt/R/src/external_arrival_poisson.R")
source("C:/Users/Bruger/Documents/P8/Projekt/R/src/OJN_simulation_manu.R")
source("C:/Users/Bruger/Documents/P8/Projekt/R/src/OJN_simulation_supplier.R")
```



## Generate leadtimes for the supplier
```{r, message = FALSE, warning = FALSE}
#Parameters
N <- 10e3  # number of events to simulate;
C <- 6          # number of nodes Department 1
K <- 6          # number of nodes Department 2
M <- 6          # number of nodes Department 3
alpha <- 0.1    # external arrival rate
mu_I <- 0.2       # Input node (I) service rate 
mu_D1 <- 0.1      # Deparment 1 (D_i^1) service rate
mu_D2 <- 0.2      # Deparment 1 (D_i^1) service rate
mu_D3 <- 0.3      # Deparment 1 (D_i^1) service rate
mu_O <- 0.5       # Output node (O) service rate

#Run generator
supplier <- generate_leadtimes_supplier(N, C, K, M, alpha, mu_I, mu_D1, mu_D2, mu_D3, mu_O)
```


## Verify the simulation
```{r}
#Total sojourn time
mean(supplier$total_time$sojourn_time)

#Plot cummulative mean
supplier$theoretical_sojourn_time

#Generate stability plot
x <- 1:N
plot(x, cumsum(supplier$total_time$sojourn_time)/x, type = "l", lty = 1)
abline(h = supplier$theoretical_sojourn_time, col="red")
```

## Generate leadtimes for the manufacturer
```{r, message = FALSE, warning = FALSE}
#Parameters
N <- 10000  # number of events to simulate;
C <- 6          # number of nodes Department 1
K <- 6          # number of nodes Department 2
M <- 6          # number of nodes Department 3
alpha <- 0.1    # external arrival rate
mu_I <- 0.2       # Input node (I) service rate 
mu_D1 <- 0.1      # Deparment 1 (D_i^1) service rate
mu_D2 <- 0.2      # Deparment 1 (D_i^1) service rate
mu_D3 <- 0.3      # Deparment 1 (D_i^1) service rate
mu_O <- 0.5       # Output node (O) service rate
pIO <- 0.9

#run generator
manufacturer <- generate_leadtimes_manufacturer(N, C, K, M, alpha, mu_I, mu_D1, mu_D2, mu_D3, mu_O, pIO)
```


## Verify the simulation
```{r}
#Total sojourn time
mean(manufacturer$total_time$sojourn_time)


#Plot cummulative mean
manufacturer$theoretical_sojourn_time


#Generate stability plot
x <- 1:N
plot(x, cumsum(manufacturer$total_time$sojourn_time)/x, type = "l", lty = 1)
abline(h = manufacturer$theoretical_sojourn_time, col="red")
```

# The distributions
```{r, message = FALSE, warning = FALSE}
# Load packages
library("ggplot2")
library("tidyverse")
```


## Histogram plots
```{r, message = FALSE, warning = FALSE}
supplier_LT_dist <- supplier$total_time %>% ggplot(aes(sojourn_time)) + geom_histogram(binwidth=1)
print(supplier_LT_dist + ggtitle("Distribution of lead times generated from supplier"))

manufacturer_LT_dist <- manufacturer$total_time %>% ggplot(aes(sojourn_time)) + geom_histogram(binwidth=1)
print(manufacturer_LT_dist + ggtitle("Distribution of lead times generated from manufacturer"))
```

